Title Goes Here

### 2025-04-17 analysis/supplementary-materials/appendix1.qmd
SOM SEM graphs finished in R ..02 Starting to add them to final SOM figs in illustrator.

@@

peaks_M24_1_1 <- do.call(rbind, peaks_list_M24_1_1)
rownames(peaks_M24_1_1) <- NULL
peaks_M24_1_1 <- peaks_M24_1_1 |> 
  filter(Counts > 250) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F", "P", "S", "Cl", "S_b", "K", "K_b"))
peaks_M24_1_1_labels <- peaks_M24_1_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b"))

@@

@@

@@

@@

peaks_M22_5.1_3 <- do.call(rbind, peaks_list_M22_5.1_3)
rownames(peaks_M22_5.1_3) <- NULL
peaks_M22_5.1_3 <- peaks_M22_5.1_3 |> 
  filter(Counts > 55) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F"))
peaks_M22_5.1_3_labels <- peaks_M22_5.1_3 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

@@

@@

@@

peaks_M22_4.1_1 <- do.call(rbind, peaks_list_M22_4.1_1)
rownames(peaks_M22_4.1_1) <- NULL
peaks_M22_4.1_1 <- peaks_M22_4.1_1 |> 
  filter(Counts > 50) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F"))

M22_4.1_1_graph <- filtered_M22_4.1_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M22_4.1_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M22_4.1_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M20_2_1 <- do.call(rbind, peaks_list_M20_2_1)
rownames(peaks_M20_2_1) <- NULL
peaks_M20_2_1 <- peaks_M20_2_1 |> 
  filter(Counts > 400) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F", "S", "Mg", "S_beta", "Ca_beta", "Ti_beta", "K_beta", "K"))

M20_2_1_graph <- filtered_M20_2_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M20_2_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M20_2_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M18_5_1 <- do.call(rbind, peaks_list_M18_5_1)
rownames(peaks_M18_5_1) <- NULL
peaks_M18_5_1 <- peaks_M18_5_1 |> 
  filter(Counts > 150) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F"))

M18_5_1_graph <- filtered_M18_5_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M18_5_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M18_5_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M18_1_1 <- do.call(rbind, peaks_list_M18_1_1)
rownames(peaks_M18_1_1) <- NULL
peaks_M18_1_1 <- peaks_M18_1_1 |> 
  filter(Counts > 200) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F"))

M18_1_1_graph <- filtered_M18_1_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M18_1_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M18_1_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M16_1_1 <- do.call(rbind, peaks_list_M16_1_1)
rownames(peaks_M16_1_1) <- NULL
peaks_M16_1_1 <- peaks_M16_1_1 |> 
  filter(Counts > 600) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F", "S_beta"))

M16_1_1_graph <- filtered_M16_1_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M16_1_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M16_1_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M15_2_s2_2 <- do.call(rbind, peaks_list_M15_2_s2_2)
rownames(peaks_M15_2_s2_2) <- NULL
peaks_M15_2_s2_2 <- peaks_M15_2_s2_2 |> 
  filter(Counts > 300) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F", "Na", "P", "S", "Cl", "K", "Ca_beta", "S_beta", "Ca", "K_beta", "Ca_L"))

M15_2_s2_2_graph <- filtered_M15_2_s2_2 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M15_2_s2_2, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M15_2_s2_2, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M15_2_s2_1 <- do.call(rbind, peaks_list_M15_2_s2_1)
rownames(peaks_M15_2_s2_1) <- NULL
peaks_M15_2_s2_1 <- peaks_M15_2_s2_1 |> 
  filter(Counts > 500) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F", "K_beta"))

M15_2_s2_1_graph <- filtered_M15_2_s2_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M15_2_s2_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M15_2_s2_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M14_4_1 <- do.call(rbind, peaks_list_M14_4_1)
rownames(peaks_M14_4_1) <- NULL
peaks_M14_4_1 <- peaks_M14_4_1 |> 
  filter(Counts > 700) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F"))

M14_4_1_graph <- filtered_M14_4_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M14_4_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M14_4_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M14_3_2_s2_1 <- do.call(rbind, peaks_list_M14_3_2_s2_1)
rownames(peaks_M14_3_2_s2_1) <- NULL
peaks_M14_3_2_s2_1 <- peaks_M14_3_2_s2_1 |> 
  filter(Counts > 60) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F"))

M14_3_2_s2_1_graph <- filtered_M14_3_2_s2_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M14_3_2_s2_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M14_3_2_s2_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

@@

peaks_M14_3_2_s1_1 <- do.call(rbind, peaks_list_M14_3_2_s1_1)
rownames(peaks_M14_3_2_s1_1) <- NULL
peaks_M14_3_2_s1_1 <- peaks_M14_3_2_s1_1 |> 
  filter(Counts > 500) |> 
  filter(!Element %in% c("Ti_L", "Mg_beta", "F"))

M14_3_2_s1_1_graph <- filtered_M14_3_2_s1_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M14_3_2_s1_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_label(data = peaks_M14_3_2_s1_1, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 3, fill = "white", label.size = 0.2, vjust = -0.5, show.legend = FALSE) +
  theme(legend.position="none")

>>>>

# ggsave("M24_1_2_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M24_1_1 <- do.call(rbind, peaks_list_M24_1_1)
rownames(peaks_M24_1_1) <- NULL
peaks_M24_1_1 <- peaks_M24_1_1 |> 
  filter(Counts > 250) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F", "P", "S", "Cl", "S_b", "K", "K_b", "Mg"))
peaks_M24_1_1_labels <- peaks_M24_1_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b"))

@@

# ggsave("M24_1_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

# ggsave("M23_7_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

# ggsave("M23_2_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M22_5.1_3 <- do.call(rbind, peaks_list_M22_5.1_3)
rownames(peaks_M22_5.1_3) <- NULL
peaks_M22_5.1_3 <- peaks_M22_5.1_3 |> 
  filter(Counts > 55) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F", "Cl"))
peaks_M22_5.1_3_labels <- peaks_M22_5.1_3 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

@@

# ggsave("M22_5.1_3_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

# ggsave("M22_5.1_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M22_4.1_1 <- do.call(rbind, peaks_list_M22_4.1_1)
rownames(peaks_M22_4.1_1) <- NULL
peaks_M22_4.1_1 <- peaks_M22_4.1_1 |> 
  filter(Counts > 50) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F"))
peaks_M22_4.1_1_labels <- peaks_M22_4.1_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M22_4.1_1_graph <- filtered_M22_4.1_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M22_4.1_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M22_4.1_1_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M22_4.1_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M20_2_1 <- do.call(rbind, peaks_list_M20_2_1)
rownames(peaks_M20_2_1) <- NULL
peaks_M20_2_1 <- peaks_M20_2_1 |> 
  filter(Counts > 400) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F", "S", "Mg", "S_b", "Ca_b", "Ti_b", "K_b", "K"))
peaks_M20_2_1_labels <- peaks_M20_2_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M20_2_1_graph <- filtered_M20_2_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M20_2_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M20_2_1_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M20_2_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M18_5_1 <- do.call(rbind, peaks_list_M18_5_1)
rownames(peaks_M18_5_1) <- NULL
peaks_M18_5_1 <- peaks_M18_5_1 |> 
  filter(Counts > 150) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F"))
peaks_M18_5_1_labels <- peaks_M18_5_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M18_5_1_graph <- filtered_M18_5_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M18_5_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M18_5_1_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M18_5_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M18_1_1 <- do.call(rbind, peaks_list_M18_1_1)
rownames(peaks_M18_1_1) <- NULL
peaks_M18_1_1 <- peaks_M18_1_1 |> 
  filter(Counts > 200) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F"))
peaks_M18_1_1_labels <- peaks_M18_1_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M18_1_1_graph <- filtered_M18_1_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M18_1_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M18_1_1_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M18_1_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M16_1_1 <- do.call(rbind, peaks_list_M16_1_1)
rownames(peaks_M16_1_1) <- NULL
peaks_M16_1_1 <- peaks_M16_1_1 |> 
  filter(Counts > 600) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F", "S_b"))
peaks_M16_1_1_labels <- peaks_M16_1_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M16_1_1_graph <- filtered_M16_1_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M16_1_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M16_1_1_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M16_1_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M15_2_s2_2 <- do.call(rbind, peaks_list_M15_2_s2_2)
rownames(peaks_M15_2_s2_2) <- NULL
peaks_M15_2_s2_2 <- peaks_M15_2_s2_2 |> 
  filter(Counts > 300) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F", "Na", "P", "S", "Cl", "K", "Ca_b", "S_b", "Ca", "K_b", "Ca_L", "Mg"))
peaks_M15_2_s2_2_labels <- peaks_M15_2_s2_2 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M15_2_s2_2_graph <- filtered_M15_2_s2_2 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M15_2_s2_2, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M15_2_s2_2_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M15_2_s2_2_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M15_2_s2_1 <- do.call(rbind, peaks_list_M15_2_s2_1)
rownames(peaks_M15_2_s2_1) <- NULL
peaks_M15_2_s2_1 <- peaks_M15_2_s2_1 |> 
  filter(Counts > 500) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F", "K_b", "Na", "Mg"))
peaks_M15_2_s2_1_labels <- peaks_M15_2_s2_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M15_2_s2_1_graph <- filtered_M15_2_s2_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M15_2_s2_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M15_2_s2_1_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M15_2_s2_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M14_4_1 <- do.call(rbind, peaks_list_M14_4_1)
rownames(peaks_M14_4_1) <- NULL
peaks_M14_4_1 <- peaks_M14_4_1 |> 
  filter(Counts > 700) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F", "P"))
peaks_M14_4_1_labels <- peaks_M14_4_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M14_4_1_graph <- filtered_M14_4_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M14_4_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M14_4_1_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M14_4_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M14_3_2_s2_1 <- do.call(rbind, peaks_list_M14_3_2_s2_1)
rownames(peaks_M14_3_2_s2_1) <- NULL
peaks_M14_3_2_s2_1 <- peaks_M14_3_2_s2_1 |> 
  filter(Counts > 60) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F"))
peaks_M14_3_2_s2_1_labels <- peaks_M14_3_2_s2_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))

M14_3_2_s2_1_graph <- filtered_M14_3_2_s2_1 |> 
  select(Energy, Counts) |>
  ggplot(aes(x = Energy, y = Counts)) +
  geom_area(fill = "snow3", alpha = 0.7) +
  geom_line(linewidth = 0.5, alpha = 0.5, linetype = "solid", colour = "#8B8989") +
  labs(x = "Energy (keV)", y = "Intensity (Counts)") +
  theme_minimal() +
  geom_point(data = peaks_M14_3_2_s2_1, aes(x = Energy, y = Counts, colour = Element), size = 3, shape = 18) +
  geom_text(data = peaks_M14_3_2_s2_1_labels, aes(x = Energy, y = Counts, label = Element, colour = Element), size = 5, vjust = -0.5, show.legend = FALSE) +
  scale_colour_manual(values = c(
  C = "#4461A8", O = "#2BACC2", F = "#3EADA9", Na = "#4FC46A", Mg = "#AEC491", Mg_b = "#AEC491", Al = "#F2C86C", Si = "#F5A838", P = "#EE850E", S = "#D54F34", S_b = "#D54F34", Cl = "#A51122", K = "#A71B4B", K_b = "#A71B4B", Ca = "#D35C79" , Ca_b = "#D35C79", Ca_L = "#D35C79", Ti = "#992766", Ti_b = "#992766", Ti_L = "#992766", Fe = "#762181" , Fe_b = "#762181" , Fe_L = "#762181")) +
  theme(legend.position="none", axis.text = element_text(size = 15), axis.title = element_text(size = 18))

# ggsave("M14_3_2_s2_1_graph.png", bg = "white" , dpi = 300, path = "analysis/figures/SOM/Graphs")

@@

peaks_M14_3_2_s1_1 <- do.call(rbind, peaks_list_M14_3_2_s1_1)
rownames(peaks_M14_3_2_s1_1) <- NULL
peaks_M14_3_2_s1_1 <- peaks_M14_3_2_s1_1 |> 
  filter(Counts > 500) |> 
  filter(!Element %in% c("Ti_L", "Mg_b", "F"))
peaks_M14_3_2_s1_1_labels <- peaks_M14_3_2_s1_1 |> 
  filter(!Element %in% c("Fe_L", "Fe_b", "Mg_b", "S_b", "K_b", "Ca_b", "Ca_L", "Ti_b", "Ti_L"))
